Geoelectric Field and Electrical Exploration Assignment: Time Sequences Signal Processing in Magnetotelluric Method

### 2024-12-27 Article/main.tex
committed by yang: Perfect the program

\begin{abstract}
    This paper presents a semester assignment on geoelectric fields and electrical prospecting conducted in the autumn semester of 2024 at Central South University. Leveraging the fundamental principles of the magnetotelluric (MT) method and statistical signal processing theory, the algorithm for time sequences processing of MT signals has been proposed. For the provided MT data, the apparent resistivity curve and phase curve were computed, along with the coherence, tilting amplitude, and phase of the measured results.
\end{abstract}

@@

\begin{equation}
    \label{tilting}
    H_z[\omega]=A_{zx}[\omega]H_x[\omega]+B_{zy}[\omega]H_y[\omega]
\end{equation}

In the same way, the tilting subvector can be calculated from Equation.\eqref{tilting}.

@@

\begin{algorithm}[H]
    \caption{Algorithm for solving the least squares estimation of the impedance tensor}
    \label{alg:z}
    \begin{algorithmic}[1]
        \Require Data of the electromagnetic field, including $f$, $E$ and $H$.
        \State Step 1: read the data from the file.
        \State Step 2: calculate the average power spectrum.
        \State Step 3: solve the least squares estimation of the impedance tensor $\mathbf{Z}$ and tilting subvectors.
        \State $\rho_\alpha=\dfrac{|Z[\omega]|^2}{2\pi f\times 4\pi\times 10^{-7}}$
        \State $\phi=\arctan\dfrac{\mathfrak{R}Z[\omega]}{\mathfrak{I}Z[\omega]}$.
        \State Step 4: calculate the apparent resistivity and phase.
        \State Step 5: save the data and plot the figures.
    \end{algorithmic}
\end{algorithm}

@@

>>>>

\begin{abstract}
    This paper presents a semester assignment on geoelectric fields and electrical prospecting conducted in the autumn semester of 2024 at Central South University. Leveraging the fundamental principles of the magnetotelluric (MT) method and statistical signal processing theory, the algorithm for time sequences processing of MT signals has been proposed. For the provided MT data, the apparent resistivity curve and phase curve were computed, along with the coherence, tipper amplitude, and phase of the measured results.
\end{abstract}

@@

\begin{equation}
    \label{tipper}
    H_z[\omega]=A_{zx}[\omega]H_x[\omega]+B_{zy}[\omega]H_y[\omega]
\end{equation}

In the same way, the tipper subvector can be calculated from Equation.\eqref{tipper}.

@@

\begin{algorithm}[H]
    \caption{Algorithm for solving the least squares estimation of the impedance tensor}
    \label{alg:z}
    \begin{algorithmic}[1]
        \Require Data of the electromagnetic field, including $f$, $E$ and $H$.
        \State Step 1: read the data from the file.
        \State Step 2: calculate the average power spectrum.
        \State Step 3: solve the least squares estimation of the impedance tensor $\mathbf{Z}$ and tipper subvectors.
        \State $\rho_\alpha=\dfrac{|Z[\omega]|^2}{2\pi f\times 4\pi\times 10^{-7}}$
        \State $\phi=\arctan\dfrac{\mathfrak{R}Z[\omega]}{\mathfrak{I}Z[\omega]}$.
        \State Step 4: calculate the apparent resistivity and phase.
        \State Step 5: save the data and plot the figures.
    \end{algorithmic}
\end{algorithm}

@@

Based on the existing algorithm, we designed and wrote the MATLAB calculation program, the specific code is as follows. The action of the first function is measured by the instrument. The electric and magnetic field strengths are read in the.AVG data.

\nolinenumbers
\lstinputlisting[caption=Read the .AVG format data file measured by the instrument., label={lst:listing-Mat}, language=Matlab]{Code/ReadAvgData.m}
\linenumbers
